---
title: "Name: Fajrun Wahidil Muharram"
author: 
- |
    | Student number: 22221082
date: "`r format(Sys.time(), '%X, %d %B, %Y')`"
output: html_document
---
# Originality declaration  

I, [**Fajrun Wahidil Muharram**], confirm that the work presented in this assessment is my own. Where information has been derived from other sources, I confirm that this has been indicated in the work.

date: `r format(Sys.time(), '%d %B, %Y')`

# Initial project scope

Research question:
How have the eviction rate in New York City evolved over the years (2017-2023), and are there discernible temporal patterns or trends in the distribution of evictions accross different boroughs and community district?

Null hypothesis:
There is no significant temporal variation in eviction rates across New York City during 2017-2023. Eviction rates remains constant over time, and any observed differences are due to random fluctuations.

# Package installing & loading

```{r install packages}
install.packages(c("tidyverse", "sf", "lubridate", "ggplot2", "here", "janitor"))
library(tidyverse)
library(sf)
library(lubridate)
library(ggplot2)
library(here)
library(janitor)
```
# Data loading
```{r load data}
# set working dictionary
here::here()

# load csv
eviction <- read_csv(here("data", "Evictions.csv"), na="NULL") 

# load the shapefile
nyc_boroughs <- st_read(here("data", "geo_export_65fab86c-efea-4868-9ae3-df21d21e1c3a.shp"))
```
# Data Exploration and Cleaning/Wrangling
```{r explore data}
# tidy the csv data
eviction <- eviction %>%  
clean_names()

# explore the csv data
Datatypelist <- eviction %>%
  summarise_all(class) %>%
  pivot_longer(everything(), 
               names_to="All_variables", 
               values_to="Variable_class")

Datatypelist

# Convert eviction data to sf object
eviction_sf <- eviction %>%
  filter(longitude<0 & latitude>0)%>%
  st_as_sf(., coords = c("longitude", "latitude"), 
                   crs = 4326)

# clean the shapefile
nyc_boroughs <- nyc_boroughs %>%
  clean_names() %>%
  st_transform(crs = 4326)

nyc_boroughs

# Perform spatial join with NYC boroughs shapefile
eviction_with_boroughs <- st_join(eviction_sf, nyc_boroughs, join = st_within)

```

```{r}
# Plot the NYC boroughs
ggplot() +
  geom_sf(data = nyc_boroughs, fill = "lightgrey", color = "red") +
  geom_sf(data = eviction_with_boroughs, aes(fill = borough), color = "blue") +
  labs(title = "Evictions Merged with NYC Boroughs",
       fill = "borough") +
  theme_minimal()

```










